noam_data_exploration_v1

### 2024-08-15 noam_data_exploration_v3.Rmd

@@

## HAD TO RUN TO CITY OFFICE FOR FAMILY SHIT AND COULDN'T FINISH THIS YET - NOAM AUG 08
# diversity_stability_site <- reduced_diversity_stability %>%
#   dplyr::group_by(island_side, site, habitat, site_habitat) %>%
#   dplyr::summarise(richness_mean = mean(richness_mean), 
#             richness_se = sd(richness_mean)/sqrt(n()),
#             richness_cv = mean(richness_cv),
#             shannon_mean = mean(shannon), 
#             shannon_se = sd(shannon)/sqrt(n()),
#             shannon_cv = CV(shannon),
#             shannon_stability = 1/CV(shannon), # Stability as defined by codyn and many others (including Pete in 2022 paper)
#             cover_mean = mean(cover),
#             cover_se = sd(cover)/sqrt(n()),
#             cover_cv = CV(cover),
#             loreau_mean = mean(loreau_synchrony),
#             loreau_se = se(loreau_synchrony),
#             portfolio_mean = mean(portfolio_effect),
#             portfolio_se = se(portfolio_effect))
#

>>>>

# algal diversity site level
diversity_site <- alpha_diversity_quad %>%
  dplyr::group_by(year, island_side, site, habitat, site_habitat) %>%
  dplyr::summarise(algae_cover_mean = mean(cover),
                   algae_cover_se = sd(cover)/sqrt(n()),
                   algae_richness_mean = mean(richness),
                   algae_shannon_mean = mean(shannon), 
                   algae_shannon_se = sd(shannon)/sqrt(n())
  )
# write_csv(diversity_site, here("data", "algae_diversity_site.csv"))

@@

# averaging from the original here to avoid taking average of average, cv of cv, etc.
diversity_cv_site <- alpha_diversity_quad %>%
  dplyr::group_by(site, habitat, island_side, site_habitat) %>%
  dplyr::summarise(algae_richness_mean = mean(richness), 
            algae_richness_se = sd(richness)/sqrt(n()),
            algae_richness_cv = CV(richness),
            algae_shannon_mean = mean(shannon), 
            algae_shannon_se = sd(shannon)/sqrt(n()),
            algae_shannon_cv = CV(shannon),
            algae_shannon_stability = 1/CV(shannon), # Stability as defined by codyn and many others (including Pete in 2022 paper)
            algae_cover_mean = mean(cover),
            algae_cover_se = sd(cover)/sqrt(n()),
            algae_cover_cv = CV(cover))

# portfolio and synchrony need to be calculated at quad level, so taking the mean of the quad level for these
synchrony_portfolio_site <- diversity_stability_quadrat %>%
  dplyr::group_by(site, habitat, island_side, site_habitat) %>%
  dplyr::summarise(
            algae_loreau_mean = mean(loreau_synchrony),
            algae_loreau_se = sd(loreau_synchrony)/sqrt(n()),
            algae_portfolio_mean = mean(portfolio_effect),
            algae_portfolio_se = sd(portfolio_effect)/sqrt(n()))

# merge together
diversity_stability_site <- merge(diversity_cv_site, synchrony_portfolio_site, by = c("site", "habitat", "island_side", "site_habitat"))
# write_csv(diversity_stability_site, here("data", "algae_diversity_stability_metrics_site.csv"))
